---
format: html
echo: false
warning: false
theme:
  dark: Superhero
---

```{r}
library(surveydown)
```

::: {#page1 .sd-page}

# Welcome to ANTH5203!

Before the semester begins, I want to get an idea of how comfortable we are with various topical areas in quantitative methods. Please address each question accordingly. You must address all questions. 

```{r}
sd_question(
  type  = 'mc',
  id    = 'grade',
  label = "What characterizes your status at ECU?",
  option = c(
    'Undergraduate Student' = 'ug',
    'Graduate Student' = 'g'
  )
)
```

```{r}
sd_next()
```

:::

::: {#page2 .sd-page}
```{r}
sd_question(
  type  = 'numeric',
  id    = 'class',
  label = "How many formal classes have you taken in mathematics, statistics, quantitative reasoning, data science, computer science, or related fields? Think back to high school, undergraduate, and/or your graduate coursework."
)
```

```{r}
sd_question(
  type  = 'textarea',
  id    = 'class_list',
  label = "List the Course Names or Topics. If '0', then put NA."
)
```

```{r}
sd_next()
```
:::

::: {#page3 .sd-page}
For each question, I want you to select how familiar you are within a given topic(s).\
\
1 = Least Familiar and 10 = Most Familiar.

```{r}
sd_question(
  type  = 'slider',
  id    = 'eda',
  label = "Exploratory Data Analysis",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_question(
  type  = 'slider',
  id    = 'probability',
  label = "Probability Theory",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_question(
  type  = 'slider',
  id    = 'nht',
  label = "Hypothesis Testing",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_question(
  type  = 'slider',
  id    = 'regression',
  label = "Regression and Causal Inference",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_question(
  type  = 'slider',
  id    = 'bayes',
  label = "Bayesian Inference",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_question(
  type  = 'slider',
  id    = 'freq',
  label = "P-Values and Confidence Intervals",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_question(
  type  = 'slider',
  id    = 'freq',
  label = "Programming Languages (i.e. R, Python, C++, etc.)",
  option = c(
    '1' = '1',
    '2' = '2',
    '3' = '3',
    '4' = '4',
    '5' = '5',
    '6' = '6',
    '7' = '7',
    '8' = '8',
    '9' = '9',
    '10' = '10'
  )
)
```

```{r}
sd_next()
```
:::

:::{#page4 .sd-page}
```{r}
sd_question(
  type  = 'textarea',
  id    = 'open',
  label = "Why are you taking this course? What do you expect to gain from this course? How can I best help you and your future research?"
)
```

```{r}
sd_next()
```

:::

::: {#end .sd-page}
Thank you for completing this survey!\
I am excited for next semester!\
Please reach out to me at wolfec23@ecu.edu should you have any concerns about the semester. 

```{r}
sd_close(label = 'Close window')
```
:::
